|

### 2021-10-14 manuscript/manuscript.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

@@

After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics. We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check. This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).     
Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs. For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Confidence, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.  
For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.     
**[Insert Figure 1 here]**  
In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). Figure 2 further clarifies the sway of multi-analyst vs. single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.  
**[Insert Figure 2 here]**  
It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa`. This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.

>>>>

Change to this:

<!-- The credibility of scientific research is in doubt, among lay consumer [@hornsey2017] and scientist [@pashler2012] alike. Several tools have been proposed to combat this "crisis of confidence" (Ibid., p. 528). One such tool is the crowd science approach: "the organization of scientific research in open and collaborative projects"  [@franzoni2014, p. 1]. We focus on crowdsourced data analysis, also known as the 'many analysts' or 'multi-analyst' approach: a crowd of scientists independently analyzes the same dataset to estimate and report on a parameter of interest.   -->
<!-- According to some of its proponents, crowdsourced data analysis should increase the credibility of scientific findings to lay consumers. In the preregistration of an ongoing many-analysts study, Arbon et al. [-@arbon2019] justify their use of the novel approach by referring to the need for "the public to have faith in the conclusions of scientists". In a preprint of a conducted multi-analyst study, Breznau et al. [-@breznau2021, p. 3] argue that independent data analyses with converging findings should offer "consumers of scientific findings assurance that they are not arbitrary flukes". In a commentary on the many analysts approach, Breznau [-@breznau2021a, p. 311], offers the hopeful view that crowdsourcing is a new way to "increase public, private, and government views of social science" and to "increase credibility for political and social research---in both sample populations and among the researchers themselves." Does crowd science meet this promise -- to improve lay perceptions of scientific findings -- in reality?   -->
<!-- We explore the effects of scientific findings emerging from a crowd of researchers (vs. a typical research collaboration) on lay consumers' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of bias and error. We compare the effects of providing lay consumers with a single parameter estimate (the single-analyst condition) vs. multiple crowdsourced parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the "multi-consistent" condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the "multi-inconsistent" condition).     -->
<!-- In line with social norm theory [@miller2016], we expect an individual who observes a crowd of scientists reach the same qualitative conclusion to be more likely to conform in opinion, and be swayed by the scientific findings, than an individual who observes the conclusion of a single scientist. Although observing several differing estimates (rather than a single estimate) may decrease lay confidence in the precise average estimate, it should increase beliefs about the reported phenomenon and decrease perceptions of bias and error. However, when laypeople observe several scientists independently come to differing qualitative conclusions, we expect the multi-analyst method to backfire; when the results generated by independent analyses vary widely and lack consensus in their qualitative conclusions, we expect a decrease in the sway of scientific findings.   -->
<!-- In sum, our preregistered hypotheses are as follows: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error. In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.  -->

@@

After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics. We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check. This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).     
Figure 1 displays the main findings of our linear regression models, which compare each condition to the single-analyst condition and control for prior beliefs. For the multi-inconsistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs, "Inconsistent")`; (b) ratings of credibility, `r results(Credibility, "Inconsistent")`; and (c) confidence in the effect size estimate, `r results(Confidence, "Inconsistent")`; and significantly higher (d) ratings of bias, `r results(Bias, "Inconsistent")`; (e) error, `r results(Error, "Inconsistent")`; and (f) discretion, `r results(Discretion, "Inconsistent")`.  
For the multi-consistent condition, we found significantly lower (a) posterior beliefs, `r results(Final_beliefs)`; significantly higher (b) ratings of error, `r results(Error)`; and (c) discretion, `r results(Discretion)`, and no significant effects on (d) ratings of credibility, `r results(Credibility)`, (e) confidence in the effect size estimate, `r results(Confidence)`, or (f) ratings of bias, `r results(Bias)`.     
**[Insert Figure 1 here]**  
In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). Figure 2 further clarifies the sway of multi-analyst vs. single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.  
**[Insert Figure 2 here]**  
It is worth noting on the basis of Figure 2 and a post-hoc, paired *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, `r t_apa`. This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms --- however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.

### 2021-10-14 poster/GSPA_Abstract.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

Word count: 699

@@

Crowd science is on the rise in behavioral science and aims to increase its credibility. Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?  
 $~~~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset. We compare the effects of providing lay consumers with a single parameter estimate vs. multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.  
 $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error. In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.

>>>>

Word count: 696

@@

Crowd science is on the rise in behavioral science and aims to increase its credibility. Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?  
 $~~~~~~~$ We focus on crowdsourced data analysis: independent scientists estimate and report a parameter from the same dataset. We compare the effects of providing lay consumers with a single parameter estimate vs. multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.  
 $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from a crowd of independent scientists, we expect -- compared to a single, non-crowdsourced estimate -- higher (lower) posterior beliefs and credibility of the results, and lower (greater) ratings of bias and error. In addition, we expect that observing differing estimates decreases confidence in the precise average parameter estimate in both multi-estimate conditions.

### 2021-10-14 poster/GSPA_Poster.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract

The **credibility of scientific research** is in doubt, among lay consumer (Hornsey & Fielding, 2017) and scientist (Pashler & Wagenmakers, 2021) alike. Several tools have been proposed to combat this "crisis of confidence" (Ibid., p. 528). One such tool is the **crowd science** approach: "the organization of scientific research in open and collaborative projects" (Franzoni & Sauermann, 2014, p. 1). We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: giving the same dataset to different teams of scientists, who independently analyze it to answer the same research question and/or estimate a parameter of interest.  
 $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019). Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve lay perceptions of scientific findings?**

@@

We explore **the effects of scientific findings emerging from a crowd of researchers** (vs. a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.  
 $~~~~~$ We compare the effects of providing lay consumers with a single, aggregate parameter estimate (the **single-analyst** condition) vs. multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition). In all three conditions, the given estimates average to 5%.

@@

We run an experiment (*N* = 1,498) with **three conditions**  
`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
A single, aggregate parameter estimate  
`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
Multiple parameter estimates with low variance and high consensus  
`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
Multiple parameter estimates with high variance and low consensus

>>>>

The **credibility of scientific research** is in doubt, among lay consumer (Hornsey & Fielding, 2017) and scientist (Pashler & Wagenmakers, 2021) alike. Several tools have been proposed to combat this "crisis of confidence" (Ibid., p. 528). One such tool is the **crowd science** approach: "the organization of scientific research in open and collaborative projects" (Franzoni & Sauermann, 2014, p. 1). We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: a crowd of scientists independently analyzes the same dataset to answer the same research question or estimate and report a parameter of interest.  
 $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019). Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve lay perceptions of scientific findings?**

@@

We explore **the effects of scientific findings emerging from a crowd of researchers** (vs. a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.  
 $~~~~~$ We compare the effects of providing lay consumers with a single parameter estimate (the **single-analyst** condition) vs. multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition). In all three conditions, we emphasize that the given estimates average to 5%.

@@

We run an experiment (*N* = 1,498) with **three conditions**  
`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
A single parameter estimate  
`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
Multiple crowd estimates with low variance and high consensus  
`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
Multiple crowd estimates with high variance and low consensus
